formula1

### 2020-02-19 inst/formula1.Rmd
time-saving: evaluate maxp(L2017) only once
timesaving: evaluate maxp(L2017) only once

```{r,maxp2017}
dotchart(maxp(L2017),pch=16,main='2017 Formula 1')
dotchart(log(maxp(L2017)[1:23]),pch=16,main='2017 Formula 1, log scale')
```

@@

m <- maxp(L2017)
ox <- rank(-points) # negative because number 1 = largest number of points
oy <- rank(-m)      # negative because number 1 = largest strength
par(pty='s')        # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

```{r,equalstrength}
L1 <- loglik(indep(equalp(L2017)),L2017)
L2 <- loglik(indep(maxp(L2017)),L2017)
pchisq(2*(L2-L1),df=25-1,lower.tail=FALSE)
```

>>>>

```{r,maxp2017}
mL2017 <- maxp(L2017)
dotchart(mL2017,pch=16,main='2017 Formula 1')
dotchart(log(mL2017)[1:23],pch=16,main='2017 Formula 1, log scale')
```

@@

m <- mL2017   # maxp(L2017)
ox <- rank(-points) # negative because number 1 = largest number of points
oy <- rank(-m)      # negative because number 1 = largest strength
par(pty='s')        # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

```{r,equalstrength}
L1 <- loglik(indep(equalp(L2017)),L2017)
L2 <- loglik(indep(mL2017),L2017)   # mL2017 == maxp(L2017)
pchisq(2*(L2-L1),df=25-1,lower.tail=FALSE)
```
